Quantifying and partitioning uncertainties in retrievals of plant traits from imaging spectroscopy data

### 2020-12-03 manuscript/manuscript.tex
Minor formatting tweaks

\authors{Alexey N. Shiklomanov\affil{1}, Shawn Serbin\affil{2}, David R. Thompson\affil{3}, Philip G. Broderick\affil{3}, and Benjamin Poulter\affil{1}}

@@

We obtained atmospherically corrected surface reflectance imaging spectroscopy data from a National Ecological Observatory (NEON) Airborne Observing Platform (AOP) scene in the Upper East River basing of Colorado, USA (39.0$^{\circ}$ N, 106.9$^{\circ}$ W) as processed by \citeA{chadwick2020integrating} and available on Google Earth Engine under the collection %\texttt{users/pgbrodrick/SFA/collections/ciacorn_priority}.
A complete description of the data and processing methods are provided in \citeA{chadwick2020integrating}.
Briefly, the scene is a mosaic from several NEON AOP flights performed in summer 2018.
NEON AOP data have a spatial resolution of XXX m and an average spectral resolution of XXX nm over the range XXX nm to XXX nm. %TODO: Fill out these values.
The atmospheric correction routine was a custom application of the Atmospheric CORrection Now (ACORN‐6LX, Imspec LLC, Glendale) software package accounting for fine-scale variation in topography and sun-sensor geometry.

We used Google Earth Engine to manually select and extract 500 vegetation pixels from this scene (Figure~\ref{fig:sitemap}).
The pixels exhibit substantial variability in brightness and spectral character:
green reflectance (550 nm) ranges from XXX to XXX;
near-infrared reflectance (1100 nm) ranges from XXX to XXX;
and hyperspectral normalized difference vegetation index (NDVI; XXX and XXX nm bands) varies from XXX to XXX (Figure~\ref{fig:input-summary}).

@@

To simulate top-of-atmosphere radiance, we used a hybrid approach recently developed by Broderick et al.~\emph{in review} (sRTMnet)that combines an atmospheric radiative transfer model (RTM) based on a computationally efficient successive orders of scattering approximation~\cite<Second Simulation of a Satellite Signal in the Solar Spectrum-Vector, 6SV, version 2.1,>{kotchenova2006validation} with a neural network-based emulator of a more advanced RTM~\cite<MODTRAN,>{berk2017validation}.

@@

\acknowledgments
The code and data for performing this analysis is permanently archived at XXXXX. % TODO
Both Isofit and the Hypertrace wrapper script are publicly developed on GitHub at https://github.com/isofit/isofit.
This work was supported by the NASA Surface Biology and Geology (SBG) mission study.
The authors declare no conflicts of interest.

>>>>

\authors{Alexey N. Shiklomanov\affil{1}, Shawn Serbin\affil{2}, David R. Thompson\affil{3}, Philip G. Brodrick\affil{3}, and Benjamin Poulter\affil{1}}

@@

\emergencystretch 2em  % Fix problematic long texttt
We obtained atmospherically corrected surface reflectance imaging spectroscopy data from a National Ecological Observatory (NEON) Airborne Observing Platform (AOP) scene in the Upper East River basing of Colorado, USA (39.0$^{\circ}$ N, 106.9$^{\circ}$ W) as processed by \citeA{chadwick2020integrating} and available on Google Earth Engine under the collection \texttt{users/pgbrodrick/SFA/collections/ciacorn\_priority}.
A complete description of the data and processing methods are provided in \citeA{chadwick2020integrating}.
Briefly, the scene is a mosaic from several NEON AOP flights performed in summer 2018.
NEON AOP data have a spatial resolution of XXX m and an average spectral resolution of XXX nm over the range XXX nm to XXX nm. %TODO: Fill out these values.
The atmospheric correction routine was a custom application of the Atmospheric CORrection Now (ACORN‐6LX, Imspec LLC, Glendale) software package accounting for fine-scale variation in topography and sun-sensor geometry.

\fussy  % Return to defaults
We used Google Earth Engine to manually select and extract 500 vegetation pixels from this scene (Figure~\ref{fig:sitemap}).
The pixels exhibit substantial variability in brightness and spectral character:
green reflectance (550 nm) ranges from XXX to XXX;
near-infrared reflectance (1100 nm) ranges from XXX to XXX;
and hyperspectral normalized difference vegetation index (NDVI; XXX and XXX nm bands) varies from XXX to XXX (Figure~\ref{fig:input-summary}).

@@

The atmospheric optical properties ($\rho_{a}$, $t$, and $s$) all vary as a function of atmospheric composition and sun-sensor geometry.
To estimate these quantities, we used a hybrid approach (sRTMnet, Brodrick et al.~\emph{in review}) that combines
an atmospheric radiative transfer model (RTM) based on a computationally efficient successive orders of scattering approximation~\cite<Second Simulation of a Satellite Signal in the Solar Spectrum-Vector, 6SV, version 2.1,>{kotchenova2006validation}
with a neural network-based emulator of a more advanced RTM~\cite<MODTRAN,>{berk2017validation}.

@@

\acknowledgments
\emergencystretch 2em
The code and data for performing this analysis is permanently archived at XXXXX. % TODO
Both Isofit and the Hypertrace wrapper script are publicly developed on GitHub at https://github.com/isofit/isofit.
This work was supported by the NASA Surface Biology and Geology (SBG) mission study.
The authors declare no conflicts of interest.

\fussy
